---
title: "SocialM"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(foreach)
library(mvtnorm)
library(LICORS)
library(readr)
library(ggplot2)
library(ggthemes)
social = read.csv("social_marketing.csv", row.names=1)
```

```{r}
sm_clean = select(social, -matches("uncategorized"))
sm_cleaned = subset(sm_clean, adult < 5)
```
The Median number of adult tags is 5, so we decide to take out data points containing more than 5 adult tweets per week. also we found out for spam, it ranges from 0-2 with mean around 0.3, so we conclude that the filter has done a pretty good job already. We not gonna touch the spam column or drop anything. Becasue uncategorized tags don't help in segmentation, we drop that whole column. 

```{r}
set.seed(1)
k_grid = seq(2, 20, by=1)
SSE_grid = foreach(k = k_grid, .combine='c') %do% {
  cluster_k = kmeans(sm_cleaned, k, nstart=50)
  cluster_k$tot.withinss
}
plot(k_grid, SSE_grid)
```
After seeing the results from k-means, we decide we will pick k = 7

```{r}
k = 7
cluster_k = kmeans(sm_cleaned, k, nstart=50)
```
K-means clustering with 7 clusters of sizes 917, 583, 475, 3533, 544, 376, 1164

```{r}
for(i in 1:k) { 
  index_temp = which(cluster_k$cluster == i)
  df_temp = sm_cleaned[c(index_temp), ]
  assign(paste("ddat",i,sep="_"),df_temp) 
  assign(paste("index",i,sep="_"),index_temp) 
} 
```
Now we have 7 different df for each cluster

###A quick try on Hie-clustering
```{r}
sm_distance_matrix = dist(social, method='euclidean')
hmin = hclust(sm_distance_matrix, method='complete')
cluster3 = cutree(hmin, k=10)
summary(factor(cluster3))
```
We have tried method "complete" and "single", also k = 5-10. The results have been disappointing because there's always one big group that takes over majority of data points. We are showing the best one we've got. So we decide to stick with results from K-means for now.

-------------------------------------------------------------------------------------------------
###PCA
We need to label each data with a group number (7 different segmentations!) for later 
The group assignments are based on results from k means
```{r}
sm_cleaned['group'] = NA

sm_cleaned$group[index_1] = 'group1'
sm_cleaned$group[index_2] = 'group2'
sm_cleaned$group[index_3] = 'group3'
sm_cleaned$group[index_4] = 'group4'
sm_cleaned$group[index_5] = 'group5'
sm_cleaned$group[index_6] = 'group6'
sm_cleaned$group[index_7] = 'group7'
```

```{r}
z = sm_cleaned[,1:35]
pc1 = prcomp(z, scale.=TRUE)
```

```{r}
loadings = pc1$rotation
scores = pc1$x
qplot(scores[,1], scores[,2], color = sm_cleaned$group, xlab = 'Component 1', ylab = 'Component 2') +scale_color_colorblind()
```

It's obvious that there are some distinct groups such as 3, 5 and 6.
Let's do some head & tail to analyze what component 1 & 2 represents.
```{r}
o1 = order(loadings[,1], decreasing = TRUE)
colnames(z)[head(o1,10)]
colnames(z)[tail(o1,10)]
colnames(z)[o1[20:25]]

o2 = order(loadings[,2], decreasing = TRUE)
colnames(z)[head(o2,10)]
colnames(z)[tail(o2,10)]
colnames(z)[o2[20:25]]
```

Seperate them into individual plots to see lcearly
```{r}
sm.group = sm_cleaned$group

qplot(scores[,1], scores[,2], facets=~sm.group, xlab = 'Component 1', ylab = 'Component 2')
```
Group3 is closer to head of PC1 and PC2 than any other groups.
"religion"      "food"          "parenting"     "sports_fandom" "school"       
"family"        "beauty"        "crafts"        "cooking"       "fashion"
 
"religion"      "sports_fandom" "parenting"     "food"          "school"       
"family"        "news"          "automotive"    "adult"         "crafts"

We conclude that this group should be more family oriented, older adults who's already married. 
-----------------------------------------------------------------------------------------------
Group6 is close to PC1 tail and PC2 middle:
 "dating"           "current_events"  "art"              "tv_film"          "college_uni"      "online_gaming"   "adult"            "spam" 
"computers"      "travel"         "tv_film"        "dating"         "current_events"
"online_gaming"

We conclude this group is close to college students, young single adults.
---------------------------------------------------------------------------------------------
Group 5 is close to tail of PC 2:
   "health_nutrition" "personal_fitness" "music"          "chatter"          "beauty"           "shopping"         "fashion"      "cooking"          "photo_sharing" 
   
We conclude this group as working woman, or our "mum" group
--------------------------------------------------------------------------------------------
Other clusters that were kinda in the middles, pretty similar:

They do contain some unique features that stood out, such as "business","small business", and "news" that were not as common as other groups. So we identify these groups as various working class, hard workers, or entrepreneur. 
