---
output:
  html_document: default
  pdf_document: default
---
```{r}
library(mosaic)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(ggpubr)
```

```{r}
flight = read.csv('ABIA.csv')
attach(flight)
names(flight)
```

```{r}
cancel = subset(flight, Cancelled == 1)
```

```{r}
table1 = xtabs(~Cancelled + CancellationCode, data = cancel)

a1 = cancel %>%
  group_by(CancellationCode) %>%
  summarize(count = sum(Cancelled))
a1

ggbarplot(a1, x = 'CancellationCode', y = 'count',
   fill = 'CancellationCode', color = 'CancellationCode', palette = "jco", label = round(a1$count)) 
```

There are a totle of 1420 cancellations. 719 of them are type A cancellations which is cancellations related to the unique carriers,. 605 of them are cancellations due to wheater (Type B), and 96 of them are NAS(Type C) which are delays or cancellations within the control of National Airspace System. 

```{r}
b1 = cancel %>%
  group_by(DayOfWeek) %>%
  summarize(total = sum(Cancelled))
b1

ggbarplot(b1, x = 'DayOfWeek', y = 'total',
   fill ='DayOfWeek', color = 'DayOfWeek', label = round(b1$total))
```

Next we plotted cancellations by days of week and found that cancellations mostly happen on Tuesdays.

```{r}
e1 = cancel %>%
  group_by(Origin) %>%
  summarize(count = sum(Cancelled))

subset(e1, Origin == 'AUS')
```

```{r}
c1 = cancel %>%
  group_by(Origin, CancellationCode) %>%
  summarize(count = sum(Cancelled))
c1
```

```{r}
Austin = subset(c1, Origin == 'AUS')
Austin
ggdotchart(Austin, x = "CancellationCode", y = "count",
           color = "CancellationCode", add = 'segment', dot.size = 6, label = round(Austin$count),
           rotate = TRUE, title = 'Austin Airport Flight Cancellations')    
```

Since we are looking at datasets in the Austin Airport. We are also interested in looking at the amount of flights that got cancelled departing from the  Austin Airport. The result shows that Austin Airport has a total of 732 cancellations and the most common cancellation type is Type A which is controlled by carrier. 

```{r}
a = sort(table(flight$Origin), decreasing = TRUE)
b =  sort(table(cancel$Origin), decreasing = TRUE)

all_air = data.frame(a)
cancel_air = data.frame(b)
merged = merge(all_air, cancel_air, by = "Var1")
merged$percentdec = merged$Freq.y/merged$Freq.x

merged$percent = (merged$percentdec)*100


merged1 = subset(merged, Freq.y != 0)
merged1
```

```{r}
merged1 = merged1[order(merged1$percent),]
merged1$Var1=factor(merged1$Var1,levels=merged1$Var1)
ggplot(data = merged1) +
  geom_bar(mapping = aes(x=factor(Var1), y=percent), stat='identity', ascending=FALSE) +
  coord_flip()
```

Finally, we are interested in looking at how Austin Airport's cancellations is compare to other airports. We normalized the number of cancellations into percentage of cancellation out of all flights in each airport, and we graphed the result. In turns out that St. Louis Airport is most frequent in canceling its flights with 6.32% cancelled flights out of all flights. Austin is actually ranked number 12th with 1.48% cancelled flights out of all flights.



