---
title: "Protfolio_exercise"
output: html_document
---

Please also see the report for more details of the portfolio, in (.pdf) format attached in the same folder!

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mosaic)
library(quantmod)
library(foreach)
```

###Develop 3 different portfolios

# First one: "Invest in China" ! not diversified, focus on 3 equities ETF and 1 money with RMB
#CQQQ: Invesco China Technology ETF
#CYB: WisdomTree Chinese Yuan Fund
#EWH:iShares MSCI Hong Kong ETF 
#CXSE: WisdomTree China ex-State-Owned Enterprises Fund
---------------------------------------------------------------------
###Extract data and adjust
```{r}
# Import a few stocks
myETF = c("CQQQ", "CYB", "EWH", "CXSE")
myprices = getSymbols(myETF, from = "2014-08-13") #five years ago
# A chunk of code for adjusting all stocks
for(ticker in myETF) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}
# Combine all the returns in a matrix
all_returns = cbind(	ClCl(CQQQa),
								ClCl(CYBa),
								ClCl(EWHa),
								ClCl(CXSEa))
all_returns = as.matrix(na.omit(all_returns))
head(all_returns)
# Compute the returns from the closing prices
```
###Doing the simulation
```{r}
# Run simulation 5000 times 
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	n_days = 20
	wealthtracker = rep(0, n_days) #initialize a list of 0
	for(today in 1:n_days) {
	  weights = c(0.25, 0.25, 0.25, 0.25) #4 ETF in total
		holdings = weights * total_wealth
		
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker[today] = total_wealth
	}
	wealthtracker
}
# Profit/loss
hist(sim1[,n_days]- initial_wealth, breaks=30, main = "Invest In China Portfolio GAIN&LOSS", xlab = "US dollar", col = "red")
```
###Compute VaR with 5% cut.
```{r}
quantile((sim1[,n_days]- initial_wealth), probs = c(0.05, 0.95))
```

-------------------------------------------------------------------------------------------------
#Portfolio Number 2:

VNG: Vanguard Real Estate Index Fund
USO: United States Oil Fund
SHV: iShares Short Treasury Bond ETF
VCSH: Vanguard Short-Term Corporate Bond ETF
JPST: JPMorgan Ultra-Short Income ETF
SCZ: iShares MSCI EAFE Small-Cap ETF
XLV: Health Care Select Sector SPDR Fund
GLD: SPDR Gold Trust

run similar simulation as previous portfolio
```{r}
myETF = c("VNQ", "USO", "SHV", "VCSH","JPST", "SCZ", "XLV", "GLD")
myprices = getSymbols(myETF, from = "2014-08-13")
for(ticker in myETF) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}
all_returns = cbind(	ClCl(VNQ),
								ClCl(USO),
								ClCl(SHV),
								ClCl(VCSH),
								ClCl(JPST),
								ClCl(SCZ),
								ClCl(XLV),
								ClCl(GLD))
all_returns = as.matrix(na.omit(all_returns))
head(all_returns)
```
```{r}
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	n_days = 20
	wealthtracker = rep(0, n_days) 
	for(today in 1:n_days) {
	  weights = c(0.125, 0.125, 0.125, 0.125,0.125, 0.125, 0.125, 0.125) #8 ETF total
		holdings = weights * total_wealth
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker[today] = total_wealth
	}
	wealthtracker
}
# Profit/loss
hist(sim1[,n_days]- initial_wealth, breaks=30, main = "Diversified Portfolio GAIN&LOSS", xlab = "US dollar", col = "blue")
```
###Compute VaR with 5% cut.
```{r}
quantile((sim1[,n_days]- initial_wealth), probs = c(0.05, 0.95))
```
-------------------------------------------------------------------------------------------------
#Portfolio Number 3:
XWEB: SPDR S&P Internet ETF 
IBUY: Amplify Online Retail ETF
JSMD: Janus Henderson Small/Md Cp Gr Alpha ETF
IFLY: ETFMG Drone Economy Strategy ETF

```{r}
myETF = c("XWEB", "IBUY", "JSMD", "IFLY")
myprices = getSymbols(myETF, from = "2014-08-13")
for(ticker in myETF) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}
all_returns = cbind(	ClCl(XWEB),
								ClCl(IBUY),
								ClCl(JSMD),
								ClCl(IFLY))
all_returns = as.matrix(na.omit(all_returns))

initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	n_days = 20
	wealthtracker = rep(0, n_days) 
	for(today in 1:n_days) {
	  weights = c(0.25, 0.25, 0.25, 0.25)
		holdings = weights * total_wealth
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker[today] = total_wealth
	}
	wealthtracker
}
# Profit/loss
hist(sim1[,n_days]- initial_wealth, breaks=30, main = "Invest In Online/Growing Industries", xlab = "US dollar", col = "green")
```
```{r}
quantile((sim1[,n_days]- initial_wealth), probs = c(0.05, 0.95))
```

